Efficient pedigree recording for fast population genetics simulation

### 2017-12-31 forwards_paper.tex
add comment on quantifying RAM use

Our method uses more RAM use than simple forward simulations (see~\ref{ss:memuse_nosel}),
although in practice shorter simplification intervals may reduce RAM use
(but at a slight cost to the speed up achieved, see~\ref{ss:seq_simp}).
The benefits to our method are not limited to situations with selection:
in a more limited set of neutral simulations we found the same qualitative
behavior with a numerically larger benefit to pedigree tracking (see~\ref{ss:speedup_nosel}).

>>>>

\jda{Maybe we should quantify the factor by which RAM use increased; it's not
	easy to read off the figures}
Our method uses more RAM (up to 2 orders of magnitude more) than simple forward simulations (see~\ref{ss:memuse_nosel}),
although in practice shorter simplification intervals may reduce RAM use
(but at a slight cost to the speed up achieved, see~\ref{ss:seq_simp}).
The benefits to our method are not limited to situations with selection:
in a more limited set of neutral simulations we found the same qualitative
behavior with a numerically larger benefit to pedigree tracking (see~\ref{ss:speedup_nosel}).
